Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-27 paper.tex
Updates from Overleaf

\includegraphics[width=0.6\textwidth]{figures/Pango_XA_nxcld_tight_graph.pdf}
\\ % &
% \multicolumn{2}{c}{
\includegraphics[width=\textwidth]{figures/Pango_XAG_nxcld_tight_graph.pdf}
% }
\end{tabularx}
\caption{\label{fig:pango-single-origin-graph}
Single origin Nextclade Pango X lineages. (A) Subgraph for XA in the long ARG: all XA samples and their ancestral lineages are shown outwards to the nearest sampled viral genome; dotted lines show where the ARG continues. Nodes are coloured by Nextclade Pango designation; smaller symbols are nodes inserted by  sc2ts (i.e. not samples); their Pango designation has been imputed where possible. (B) Details for the single-origin Pango X lineages in the long ARG. (C) XAG origins in the long ARG.}
\end{figure}

@@

In Figure~\ref{fig:multiple_origins_graph} we give the details of these multiple pango lineages, along with an example lineage subgraph. The  earliest descendant sample of each of these putative independent XD origination nodes has EPI\_ISL: 11222324 (dated 2022-02-26) for the left hand plot, and EPI\_ISL 8514045 (dated 2021-12-30) for the right hand one. These two samples differ by  Supplementary Figure~\ref{fig:pango_XD_gisaid_graph} shows the equivalent subgraph with sample identifiers and GISAID Pango labels, none of which are XD (there are no samples designated by GISAID as XD in the long ARG).

>>>>

\includegraphics[width=0.6\textwidth]{figures/Pango_XA_nxcld_tight_graph.pdf}
\\ % &
% \multicolumn{2}{c}{
\includegraphics[width=\textwidth]{figures/Pango_XAG_nxcld_tight_graph.pdf}
% }
\end{tabularx}
\caption{\label{fig:pango-single-origin-graph}
Single origin Nextclade Pango X lineages. (A) Subgraph for XA in the long ARG: all XA samples and their ancestral lineages are shown outwards to the nearest sampled viral genome; dotted lines show ARG continuation. Nodes are coloured by Nextclade Pango designation; smaller symbols are non-sample nodes inserted by sc2ts, with imputed Pango status. (B) Details for the single-origin Pango X lineages in the long ARG. (C) XAG origins in the long ARG.}
\end{figure}

@@

In Figure~\ref{fig:multiple_origins_graph} we give the details of these multiple pango lineages, along with an example lineage subgraph. In this XD example the left hand subgraph (the origin of three XD samples) has an earliest sample with EPI\_ISL: 11222324 (dated 2022-02-26), while the right hand subgraph has a single sample with EPI\_ISL 8514045 (dated 2021-12-30). These two samples differ by 35 mutations; considering the time between the samples, it does seem possible that they represent true independent origins of XD. Supplementary Figure~\ref{fig:pango_XD_gisaid_graph} shows the same subgraphs with sample identifiers and coloured by GISAID Pango labels (however, no samples are designated by GISAID as XD in the long ARG).
